Assessment of zonally symmetric and asymmetric components of the Southern Annular Mode using a novel approach

### 2023-03-28 analysis/paper/asymsam.Rmd
Adds pure html output

bibliography: 
  - AsymSAM
  - packages
bibstyle: spbasic
# bibstyle options spbasic(default), spphys, spmpsci
output: 
  bookdown::pdf_book: 
      base_format: rticles::springer_article
      latex_engine: "xelatex"
      citation_package: "natbib"
      # pandoc_args: ["--lua-filter=abstract-to-meta.lua"]
header-includes: 
 - \usepackage{gensymb}
 - \usepackage{subfig}
#  - \usepackage[inline]{showlabels}
 - \usepackage{chngcntr}
 - \usepackage{natbib}
 - \usepackage{lineno}
 - \linenumbers 
---

```{r setup, echo = FALSE,warning=FALSE, message = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.path = "",
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  cache.extra = 43,
  cache.path = "../cache/",
  collapse = TRUE,
  comment = "#>",
  dev = c("pdf", "png"),
  dpi = 300,
  out.extra = ""
)

>>>>

bibliography: 
  - AsymSAM.bib
  - packages.bib
bibstyle: spbasic
# bibstyle options spbasic(default), spphys, spmpsci
output: 
  # bookdown::html_document2:
  #     code_folding: "hide"

  bookdown::pdf_book: 
      base_format: rticles::springer_article
      latex_engine: "xelatex"
      citation_package: "natbib"
      # pandoc_args: ["--lua-filter=abstract-to-meta.lua"]

header-includes: 
 - \usepackage{gensymb}
 - \usepackage{subfig}
#  - \usepackage[inline]{showlabels}
 - \usepackage{chngcntr}
 - \usepackage{natbib}
 - \usepackage{lineno}
 - \linenumbers 
---

```{r setup, echo = FALSE,warning=FALSE, message = FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  fig.path = "",
  message = FALSE,
  warning = FALSE,
  cache = TRUE,
  cache.extra = 43,
  cache.path = "../cache/",
  collapse = TRUE,
  comment = "#>",
  dev = if (knitr::is_html_output()) c("png") else c("pdf", "png"),
  dpi = 300,
  out.extra = ""
)
